\newpage
\section{Introduction}
\pagenumbering{arabic}

\subsection{Background}
Stock is a share in the ownership of a company. Stock represents a claim on the company's assets and earnings. Stocks are issued by the company itself so that it can raise money by selling a small fraction of it. Issuing stock is advantageous for the company because it does not require the company to pay back the money to some party/bank. The buying and selling of the stocks is done in a stock market.\\

Stock market and its trends are extremely volatile in nature in the finance field. It attracts researchers to capture the volatility and predicting its next moves. Investors and market analysts study the market behavior and plan their buy or sell strategies accordingly. The overall operation of stock market is based on the concept of demand and supply. If demand for a company's stock is higher in the market then the company's share prices move in upward direction. Likewise if the demand for the company's stock is very low compared to the supply then it is obvious that the company shares will be dealt in lower price. This is the basic principle behind the operation of stock market.\\

A stock exchange is an exchange where stock-brokers and traders can buy and/or sell stocks (or shares), bonds and other securities. Companies may want to get their stock listed on a stock exchange. Other stocks may be traded "over the counter", that is, through a dealer. A large company will usually have its stock listed on many exchanges across the world. Some exchanges are physical locations where transactions are carried out on a trading floor, by a method known as open outcry. This method is used in some stock exchanges and commodity exchanges, and involves traders entering oral bids and offers simultaneously. An example of such an exchange is the New York Stock Exchange(abbreviated as NYSE). The other type of stock exchange is a virtual kind, composed of a network of computers where trades are made electronically by traders. An example of such an exchange is the NASDAQ.\\

The Nepal Stock Exchange Limited (abbreviated as NEPSE) is the only Stock Exchange of Nepal. It is located in Singha Durbar Plaza, Kathmandu Nepal. The basic objective of NEPSE is to impart free marketability and liquidity to the government and corporate securities by facilitating transactions in its trading floor through member, market intermediaries, such as broker, market makers etc.\\

The stock market can be viewed as a particular data mining and artificial intelligence problem. The movement in the stock exchange depends on capital gains and losses and most people consider the stock market erratic and unpredictable. However, patterns that allow the prediction of some movements can be found. Stock market analysis deals with the study of these patterns. It uses different techniques and strategies, mostly automatic that trigger buying and selling orders depending on different decision making algorithms. It can be considered as an intelligent treatment of past and present financial data in order to predict the stock market future behavior. Therefore it can be viewed as an artificial intelligence problem in the data mining field.\\

But, stock market prediction comes with a challenging question of whether the stock price is predictable or not? So, the random walk hypothesis states that the price of stock is collocated by a random walk and hence the stock market is unpredictable. The debate about whether the stock market can be predicted or not has lasted for many years, but there has not been a consensus yet. However, many researchers have built their own stock price predicting systems, to some extent, for proving the stock market's predictability.\\

\subsection{Objectives}
The main objectives of this projects are as follows :\\
 1. To predict the stock market trend based on technical, fundamental and news-sentimental analysis\\
2. To visualize the prediction results and daily trading prices in the form of interactive charts\\
3. To compare the results and effectiveness of each algorithm with another\\

\subsection{Problem Statement}
Theoretically, the stock market is said to be very difficult to predict, due to its dynamic and non-linear model. However, the investors and stock analysts have been trying to somehow predict the stock prices of a company, to increase the profit in buying and selling stocks. Appreciable efforts have also been made from academic researchers and enthusiasts in this field. However, identifying the pattern of such an uncertain system through simple calculations and mathematics results in poor accuracy with questionable reliability. Complex, dedicated systems and models are required which can take into consideration, the numerous factors that can affect the stock price of a company. For an instance, the intrinsic valuation of a company and its performance in the market till now are equally important factors in determining its future price. However, it is very difficult to know for certain which factor affects the most at the given time, and by how much. Therefore, the market should be analyzed under various influencing factors, the prime of which are: Technical factors, Fundamental factors and News-sentimental factors. In technical analysis, the prediction model is built considering a companys past performance in the stock market, which includes studying the past rise and fall trends, average traded volumes, bullish trend behaviors and so on. In fundamental analysis, the worth of the company, its current profits, capital gains and the future profits plays a vital role in understanding its stock price behaviors. In news-sentiment analysis, the immediate effects of political, economic and stock related news in a companys stock prices is studied and applied. \\

Therefore, through circumstantial application of above mentioned analysis, this projects presents a general and complete solution for stock prediction, which can be employed in the real world for gaining profit in the stock market.

\subsection{Scope of project}
The project aims to predict the stock trend movements of trading companies based on large volume of historical data collected from various sources. The historical data constitutes of a companys fundamental valuations, past trading prices and volumes, and past news features. The basic driving factors for choosing a prediction model is its effectiveness, applicability and accuracy of results. By using multiple analysis and prediction models, the project aims to compare the usability of each such models. On completion of this project, we aim to establish a highly reliable stock prediction system, which can be used by investors to decide when to buy or sell the stocks of a company in order to gain maximum profit. It is hoped that the project will be beneficial for the stakeholders including, researchers, business analysts, stock market enthusiasts and policy makers. The project is also focused on improving the trading experience of new investors who may or may not know much about the market behaviors. 
