\section{SCOPE OF PROJECT}
The work focuses on analyzing the past history(data) of a company and its trend allowing user to compare between different companies. Also, the prediction for the following day are done based on the historical data pattern. The primary users of the system will be Investment Banks and general public who wish to know the market trend and future value of some stocks. The scope of the work can be explained in two different scenarios. They are mentioned below:

\begin{enumerate}
	\item \textbf{View point of Investment Banks: }Financial companies like Investment Banks place their capital risk by buying all the securities from the company at a discounted price. Bankers then mark up the securities to market retail price and sell them to the investing public. If the sale of securities does not reach the target capital requirement, bankers are forced to borrow from commercial banks or sell the shares at a loss. Thus, there is a need for Investment bank to analyze the company before taking any risk. We have built a system that can help investment banks do the required risk analysis.
	\item \textbf{View point of general public: }People have  always been looking forward to invest on companies with minimal risk and high gain assurance. Generally, here in Nepal, the investments on companies are more based on rumors than self-judgment. More importantly, people are ignorant of the working of stock market, and more often many do not last long in the stock investing business due to persistent failure. Our system aims to provide the required information to check the recent growth of companies and help general public evaluate and invest on fruitful companies. 
Also, the system can be used to make a basic assumption on what the stock price is going to be the following day. 

\end{enumerate}
